### 2024-05-16 Conclusion.tex
Adding minor corrections from viva/annotated thesis

Chapters~\ref{chap:1layer} and \ref{chap:2layer} evaluate the prominent single and double analytical tissue models respectively using both simulated and measured spectra. These chapters demonstrated that the Yudovsky 2009 and Jacques 1999 single layer models were highly effective in analysing data for homogeneous semi-infinite tissues, whilst the Modified Beer-Lambert single layer model and Yudovsky 2009 double layer models must be used with caution.

@@

\subsection{Computational processing improvements}
Both the novel synthetic white balancing algorithm in Chapter~\ref{chap:SWB} and the pixel-by-pixel processing in Chapter~\ref{chap:HSImodel} could benefit from improved computational processing times for better integration into surgical workflow. In both cases, parallelisation using GPU processing could be utilised to shorten the time required for these tasks. The processing in Chapter~\ref{chap:HSImodel} could also be improved further by utilising deep learning methods. After validation of high quality results using an analytical model when used to analyse neurosurgical data, the model could be used to generate training data for a neural network to be trained with. This could result in a neural network capable of providing similar quality results in a much shorter processing time. This network, however, will not be able to exceed the quality of the model used to provide the training data and so the results using the analytical models themselves should first be improved.

>>>>

Chapters~\ref{chap:1layer} and \ref{chap:2layer} evaluate the prominent single and double layer analytical tissue models respectively using both simulated and measured spectra. These chapters demonstrated that the Yudovsky 2009 and Jacques 1999 single-layer models were highly effective in analysing data for homogeneous semi-infinite tissues, whilst the Modified Beer-Lambert single-layer model and Yudovsky 2009 double-layer models should be used with caution.

@@

\subsection{Computational processing improvements}
Both the novel synthetic white balancing algorithm in Chapter~\ref{chap:SWB} and the pixel-by-pixel processing in Chapter~\ref{chap:HSImodel} could benefit from improved computational processing times for better integration into surgical workflow. In both cases, parallelisation using GPU processing could be utilised to shorten the time required for these tasks. The processing in Chapter~\ref{chap:HSImodel} could also be improved further by utilising deep learning methods. After validation of high quality results using an analytical model, the model could be used to generate training data for training of a neural network. This could result in a neural network capable of providing similar quality results in a much shorter processing time. This network, however, will not be able to exceed the quality of the model used to provide the training data and so the results using the analytical models themselves should first be improved.
